Detailed Geant4 simulations of the ANITA and ANITA-CUP neutron facilities

### 2015-04-20 Paper2015.tex
Checked and corrected proton current (215nA) and corresponding integral fluence rate values.

\subsection{Neutrons}
Fig.~\ref{fig:SUPDensity} shows neutron distribution at the SUP, for neutrons above \SI{10}{\MeV}.
The collimator ensures that the beam is circular. Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{7.6e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{1.0e6}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2009}.
The present calculations therefore underestimate measurements at the SUP by 24\%.
\todo{Check SUP fluence rates.}
\todo{Give SUP fluence rates to 3 s.f.}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.9\columnwidth]{CUPTOF10beamproRADECS.eps}
    \caption{
        Vertical profile of \U238\ fission events at the CUP.
        Dashed lines indicate expected quasi-collimation by the target surroundings.
    }
    \label{fig:CUPProfile}
\end{figure}

Fig.~\ref{fig:CUPDensity} shows the spatial distribution of neutrons above \SI{10}{\MeV} at the CUP.
As CUP is upstream of the collimator the distribution is not circularly symmetric.
In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{8.44e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
The present results underestimate measurements at the CUP by 28\%.
\todo{Check CUP fluence rates.}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{CUPTOFtofspectraRADECS.eps}
    \caption{
        Time of flight spectra for \U238 fission events at the CUP-TOF position, with \SI{3}{\cm} diameter collimator.
        }
    \label{fig:TOFSpectra}
\end{figure}

>>>>

\subsection{Neutrons}
Fig.~\ref{fig:SUPDensity} shows neutron distribution at the SUP, for neutrons above \SI{10}{\MeV}.
The collimator ensures that the beam is circular. Within the beam umbra the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{7.05e5}{\neutron\per\cm\squared\per\second}, compared to \SI{6.38e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt2013} and \SI{1.0e6}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2009}.
The present calculations therefore underestimate measurements at the SUP by 30\%.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.9\columnwidth]{CUPTOF10beamproRADECS.eps}
    \caption{
        Vertical profile of \U238\ fission events at the CUP.
        Dashed lines indicate expected quasi-collimation by the target surroundings.
    }
    \label{fig:CUPProfile}
    \todo{Fig.~\ref{fig:CUPProfile}: add axis labels.}
\end{figure}

Fig.~\ref{fig:CUPDensity} shows the spatial distribution of neutrons above \SI{10}{\MeV} at the CUP.
As CUP is upstream of the collimator the distribution is not circularly symmetric.
In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{7.85e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
The present results underestimate measurements at the CUP by 33\%.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{CUPTOFtofspectraRADECS.eps}
    \caption{
        Time of flight spectra for \U238 fission events at the CUP-TOF position, with \SI{3}{\cm} diameter collimator.
        }
    \label{fig:TOFSpectra}
    \todo{Fig.~\ref{fig:TOFSpectra}: correct axis labels.}
\end{figure}
